\labday{12 April 2023}

\experiment{MAZ04}

\begin{itemize}
\item UCASS-AA-MAZ04-001 has become UCASS-AD-MAZ04-001 due to incorrect gain. Resistor gain pair was replaced with 330K, 6.5p.
\item Measurement leads were taped up.
\item The cases are marked with L for leaded or U for unleaded
\item Some covers had to be re-stuck with tape
\item Some were marked, some were not...
\item Cases are marked with tape for now
\end{itemize}

\textbf{Aerosol Calibration:}

The calibration was set up as follows. The clean bottle was washed thouroughly with IPA, as was the aerosol transportation apparatus. The comprossor was attached to the sample bottle, as was the filter for the air. An aerosol mode UCASS (FMI02-001) was connected to the aerosol outlet, and the compressor was run until the unit registered few counts. After \SI{30}{\second} of sampling the max count number before 50 ADC was 7, and after was 3. A new filter was opened, and this took several attempts to achieve. The air was much cleaner with the filter.

A small amount of calibration standwar was put in the aerosol bottle, and the compressor was run through it for \SI{15}{\second}. The UCASS laser was left to warm up for a minute before collecting samples. It was found the sample had to be refreshed every 5-6 runs.

Datapoints taken were as follows:
\begin{itemize}
\item \SI{3}{\micro\metre} Silica (aerosol)
\item \SI{4.5}{\micro\metre} Silica (both) --> ~200ADC, ~60ADC
\item \SI{11.58}{\micro\metre} Glass (both)
\item \SI{25.6}{\micro\metre} Glass (droplet)
\end{itemize}

Calibration notes:
\begin{itemize}
\item UCASS-AD-MAZ04-009 registers no counts with droplet spray, check tomorrow
\item UCASS-AD-MAZ04-011 registers no counts with cali, and all counts in 1st bin with droplet gun, check tomorrow
\end{itemize}
